### 2024-06-12 basic-statistics.qmd
20240610 - clarification
20240612 - interactive statistical decision tree

@@

>>>>

For instance, points in football has order, equally spaced intervals, and an absolute zero—a team cannot score less than zero points, and zero points reflects absence of points (though it could be argued to be interval data because zero points does not reflect absence of skill.)

@@

For an online, interactive statistical decision tree to help you decide which statistical analysis to use, see here: <https://www.statsflowchart.co.uk>
